Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 revise/revise.tex
Add to revise.tex about mesh convergence. Closes #41

\question It is not clear how the domain is discretized. Is there a radial
discretization in graphite and channels? Was the mesh convergence checked?
Please discuss.
\begin{solution}
       <++>
\end{solution}

>>>>

\question It is not clear how the domain is discretized. Is there a radial
discretization in graphite and channels? Was the mesh convergence checked?
Please discuss.
\begin{solution}
       The following passage has been added:

       The 2D mesh has a characteristic size of 10 cm in the axial
       direction and .4 cm in the radial direction to capture the variation from moving
       between fuel and moderator subdomains. Solution time on the resulting 1960
       element, 8697 DOF problem is a couple minutes on a single core. Solving on a
       mesh uniformly refined three times yields the same qualitative behavior
       described in the results that follow for the coarse mesh. Additionally the 3x
       refinement yielded only a 1 K change in the average reactor temperature; thus,
       the coarse mesh results are regarded as sufficiently converged.
\end{solution}
